---
title: "LTN"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(XML)
library(RCurl)
library(httr)
library(rvest)
library(xml2)
library(dplyr)
stringsAsFactors = TRUE
```

## 自由時報ltn

url:https://news.ltn.com.tw/search/?keyword=%EF%BC%8C%20%E3%80%82&conditions=or&SYear=2018&SMonth=9&SDay=24&EYear=2018&EMonth=11&EDay=24&page=1
page從1~3381
類別：xpath <- "//*[contains(concat( " ", @class, " " ), concat( " ", "chan", " " ))]"
時間：xpath <- "//*[(@id = "newslistul")]//span"
標題：xpath <- "//*[contains(concat( " ", @class, " " ), concat( " ", "tit", " " ))]"


#page1
```{r cars}
doc <- read_html("https://news.ltn.com.tw/search/?keyword=%EF%BC%8C%20%E3%80%82&conditions=or&SYear=2018&SMonth=9&SDay=24&EYear=2018&EMonth=11&EDay=24&page=1") 
title <- doc %>% 
  html_nodes(xpath = "//*[contains(concat( \" \", @class, \" \" ), concat( \" \", \"tit\", \" \" ))]//p") %>% html_text()
title
date <- doc %>%
  html_nodes(xpath = "//*[(@id = \"newslistul\")]//span")%>% html_text()
date
genre <- doc %>%
  html_nodes(xpath = "//*[@id=\"newslistul\"]/li/a[1]") %>% 
  html_text()
genre

df <- data.frame(genre,date,title)

```

##forloop

```{r pressure, echo=FALSE}

df <- data.frame(genre,date,title)
for(p in 2:3381){
    url <- paste0("https://news.ltn.com.tw/search/?keyword=%EF%BC%8C%20%E3%80%82&conditions=or&SYear=2018&SMonth=9&SDay=24&EYear=2018&EMonth=11&EDay=24&page=",p)
    doc <- read_html(url) 
title <- doc %>% 
  html_nodes(xpath = "//*[contains(concat( \" \", @class, \" \" ), concat( \" \", \"tit\", \" \" ))]//p") %>% html_text()
date <- doc %>%
  html_nodes(xpath = "//*[(@id = \"newslistul\")]//span")%>% html_text()
genre <- doc %>%
  html_nodes(xpath = "//*[@id=\"newslistul\"]/li/a[1]") %>% 
  html_text()
    temp.df <- data.frame(genre,date,title)
    df <- bind_rows(df, temp.df)
    print(paste(p, nrow(df)))
}
df
library(jsonlite)
ltn.json <- toJSON(df)
save(df, file="ltn_all.rda")
write.csv(df,file="ltn_all.csv")
```

##politicals
```{r}
class(df)
str(df)
df_politicals <- df[df$genre == "政治",]
ltn_political.json <- toJSON(df_politicals)
save(df_politicals, file="df_politicals.rda")
write.csv(df_politicals,file="df_politicals.csv")
```

